Untitled

### 2018-08-12 MSOAmodel.Rmd
Simplify Bootstrapping
I refactored the code for bootstrapping and sampling. This made it easier to understand and allowed me to have a single strapping function that can be modified for high or low memory usage.
I also fine tuned the quantiles

```{r}
PriceCounts <-prices %>%
  filter(X5 %in% c("D", "S", "T", "F")) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n()) %>%
  arrange(counts)

PriceCounts<- EW2 %>%
  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
  left_join(.,PriceCounts, by = "LSOA11CD") %>%
  mutate(counts = ifelse(is.na(counts), 0, counts),
         Homes2 = Homes/10) %>%
  filter(counts!=0)

#Create a list of vectors by LSOA
setwd(basewd)
 LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
   print(.x)
    prices %>%
      filter(LSOA11CD==PriceCounts$LSOA11CD[.x], 
             X5 %in% c("D", "S", "T", "F")) %>%
      pull(X2)
 })

 names(LSOAPriceList) <- PriceCounts$LSOA11CD
saveRDS(LSOAPriceList, "LSOAPriceList2.rds")

@@

@@

StratifiedBoot <- function(dataList, LSOAcode, SamplesVect, samples = 1000){
  #datadf
 1: samples %>% map_df(~{
   print(.x)
  SubData <- 1:length(LSOAcode) %>% map(~{
    #print(.x)
    dataList[[LSOAcode[.x]]] %>%
      sample(., SamplesVect[.x], replace = TRUE)

    }) %>% unlist

  SubData%>%
       quantile(.) %>% t %>% as.data.frame %>% setNames(names(.) %>% make.names) %>%
      mutate(mean = mean(SubData),
             ID = .x)
 }) 
}

#Subset list to only the LADs used in analyis
LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
PriceCounts2 <- PriceCounts %>%
  filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))

AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)
setwd(basewd)

@@

```{r}
LupPerc <- ls(pattern= "DATA") %>% map_df(~{
  get(.x) %>% select(MSOA11CD, LowUse, Homes)

}) %>%
  group_by(MSOA11CD) %>%
  summarise_all(sum) %>%
  mutate(LowUsePerc = LowUse/(LowUse+Homes),
         Q1 = LowUsePerc>0.033,
         Q2 = LowUsePerc>0.02,
         Top90 = LowUsePerc>0.058)

#Top quartile of LUPS
quantile(LupPerc$LowUsePerc)
quantile(LupPerc$LowUsePerc, prob = seq(0, 1, length = 11))

MSOABootQuartiles2 <- MSOABootQuartiles %>%
   select(-X0.,-X100.) %>%
   group_by(MSOA11CD) %>%
   summarise_all(funs(mean, sd)) %>%
   mutate(X25Perc = X25._sd/X25._mean,
          X50Perc = X50._sd/X50._mean,
          X75Perc = X75._sd/X75._mean)  %>%
   left_join(., EW2%>%
               select(MSOA11CD, LAD11CD, LAD11NM) %>% distinct()) %>%
   left_join(., IncomeEst) %>%
   select(MedianPrice=X50._mean, Yearly.income, MSOA11CD, LAD11CD, LAD11NM)  %>%
  left_join(LocalAfford, by = "MSOA11CD") %>%
  left_join(LupPerc, by = "MSOA11CD")%>%
  filter(!is.na(LowUse)) %>%
   mutate(AffordRatio = MedianPrice/Yearly.income,
          AffordLocalRatio = AffordRatio/LocalAfford,
          AffordRank = percent_rank(AffordRatio),
          AffordLocalRank = percent_rank(AffordLocalRatio),
          LowUseRank = percent_rank(LowUse)>0.75)

MSOABootQuartiles2 %>%
  ggplot(aes(x= AffordRatio , y = AffordLocalRatio, colour = LowUseRank)) + geom_point()

@@

#Quadrant

```{r}
  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
                                    summarise(MedianHomes = first(MedianHomes),
                                              MeanHomes = first(MeanHomes),
                                              MedianLUPs = first(MedianLUPs),
                                              MeanLUPs = first(MeanLUPs),
                                              LAD11CD= first(LAD11CD),
                                              HighVal = sum(HighVal),
                                              Homes = sum(Homes),
                                              LowUse = sum(LowUse)) %>%
                                    group_by(LAD11CD) %>%
                                    summarise_all(., mean, na.rm = TRUE) %>%
                                      select(-ID)
  )

BootDeets2 <- BootDeets %>%
  mutate(MedianPercDiff = (MedianLUPs-MedianHomes)/MedianHomes,
         PercLowUse = LowUse/Homes,
         RankLowUse = percent_rank(PercLowUse),
         RankMedianDiff = percent_rank(MedianPercDiff),
         Catagory = case_when( 
           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
           TRUE ~ 4 #Low low use low price difference
         ) %>% as.factor)%>%
  left_join(EW2 %>%
  group_by(LAD11CD, LAD11NM) %>%
  summarise(TotMSOA = n(),
         Homes = sum(Homes)) %>%
  arrange(-TotMSOA) %>%
  summarise(TotMSOA = first(TotMSOA),
            LAD11NM = first(LAD11NM)), by = "LAD11CD")

BootDeets2 %>%
  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Catagory)) + geom_point()

test <- MSOABootQuartiles2 %>%
  left_join(select(BootDeets2, LAD11CD, Catagory), by = "LAD11CD")

 %>%
  ggplot(aes(x= AffordRank , y = AffordLocalRank, colour = Catagory)) + geom_point()

@@

>>>>

#Create a data frame of LSO
PriceCounts <-prices %>%
  filter(X5 %in% c("D", "S", "T", "F")) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n()) %>%
  arrange(counts)
##The subsampling is 1/10 of the number of homes in each LSOA, this stops crashes
PriceCounts<- EW2 %>%
  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
  left_join(.,PriceCounts, by = "LSOA11CD") %>%
  mutate(counts = ifelse(is.na(counts), 0, counts),
         Homes2 = Homes/10) %>%
  filter(counts!=0)

#Create a list of price vectors by LSOA
#This process can take a while
setwd(basewd)
if(file.exists("LSOAPriceList2.rds")){

@@

}else{

  LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
   print(.x)
    prices %>%
      filter(LSOA11CD==PriceCounts$LSOA11CD[.x], 
             X5 %in% c("D", "S", "T", "F")) %>%
      pull(X2)
    })
  names(LSOAPriceList) <- PriceCounts$LSOA11CD
  saveRDS(LSOAPriceList, "LSOAPriceList2.rds")

}

if(file.exists("AllDataQuartiles.rds")){

  AllDataQuartiles <- readRDS("AllDataQuartiles.rds")

}else{
  #Subset list to only the LADs used in analyis
  LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
  PriceCounts2 <- PriceCounts %>%
    filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))

  AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)

  rm(list = c("LSOAPriceList2", "PriceCounts2"))

}

rm(LSOAPriceList)

AllDataQuartilesSummary <- AllDataQuartiles %>%
  summarise_all(funs(mean, sd))

BasicQuartiles <- prices$X2 %>% .[prices$LAD11CD %in% unique(DATAdf$LAD11CD)] %>% quantile(.)

#difference between the two up to 8% this has knock on effects later in the analysis if the quartiles are not calculated correctly
AllDataQuartilesSummary[2:4]/BasicQuartiles[2:4]

prices <- prices %>%
  mutate(CountryClass = cut(X2, AllDataQuartilesSummary[2:4] %>% c(0,., Inf), 
                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
                              right = F) %>% fct_relevel(., "Upper", after = 3))

rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary)

@@

@@

#Complex models

These models work at MSOA level only and include data from the LAD level
Tehy are rubbish so aren't included in the main work. Just kept here so I don't forget I have already checked.

DATAdf %>%
  arrange(LAD11NM) %>% pull(LAD11NM) %>% unique

MSOAMean2 <-MSOAMean %>%
  mutate(RelativeAfford = AffordRatio/LADAffordRatio,
         RelativeTourismDens = TourismDensity/LADTourismDensity,
         RelativeTourismDens = ifelse(is.finite(RelativeTourismDens), RelativeTourismDens, 100)) %>%
  filter(!is.na(HighVal)) #Temporary  until I work out how to get rid of those weird MSOA

KitchenSink <- as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2+ RelativeAfford +RelativeTourismDens+
                            LADTourismDensity+ LADAffordRatio+ LADAffordRatio2)

KitchenSink2 <- as.formula(Reference ~RelativeAfford +RelativeTourismDens+
                            LADTourismDensity+ LADAffordRatio)
Formulas2 <- c(as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2),
               KitchenSink)

set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean2 , c(test = 0.2, train = 0.8)))

MSOAModels2 <-LinearClassifierCombiner(MSOAMean2,  Outcomes, Formulas2, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           LAD = grepl("LAD", Formula)
         )

#No difference
MSOAModels2 %>%
  group_by(Dependent, IncAfford2, LAD) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            ) %>%
  ungroup %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value"))

library(ranger)

#Just under 78% better than all other models
ResOut <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>% 
  TreeResampledModelPerf(., TestResample, KitchenSink)

ResOut2 <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>%
  TreeResampledModelPerf(., TestResample, KitchenSink2)

ResOut %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

ResOut2 %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

@@

```{r}
#This model uses information from the over all LUP as a result I need to subset the data by lups then train on the MSOA
set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))

ComplexModels <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink, CombineData = TRUE) %>%
      mutate(Dependent = .x)
})

ComplexModels %>%
  group_by(Dependent) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

KitchenSink2 <- as.formula(Reference ~RelativeAfford +RelativeTourismDens+
                            LADTourismDensity+ LADAffordRatio)

ComplexModels2 <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink2, CombineData = TRUE) %>%
      mutate(Dependent = .x)
})

ComplexModels2 %>%
  group_by(Dependent) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

Modeldf <-MSOAMean2 %>%
      rename_(Reference = "LADHighLUP")

@@

#Collaspy tree voting
```{r}

test <- MSOAMean2 %>%
      rename_(Reference = "LADHighLUP") %>%
MSOATreeVoting(., TestResample, KitchenSink )

test %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )
